---
title: "My first R package"
author: "Radhika Srivastava"
date: 2015-07-23T21:13:14-05:00
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
---



## The Conversion Package

When creating my first package in R, I wanted to make a something that would make truly be useful and have adequate functionality. Over the past few weeks I have been in Cape Town, I realized that it would be useful to have a tool to convert standard units used in America, to metric units used in South America (and the rest of the world). So, I decided to make a R package that would do just that. 

Here is the code for the function that I used to make my package:

```{r}
conversion <- function(type,value)
  {
  if(type=="w")
  {print("Weight Conversion")
    return(value * 0.453592)}
  else if(type=="d")
  {print("Distance Conversion")
    return(value * 0.3048)}
  else if (type=="t")
  {print("Temperature Conversion")
      return((value-32)*.5556)}
  else {
    (print("Invalid Conversion Type"))
    return (-1)
  }
}
```

# Including Plots

You can also embed plots. See Figure \@ref(fig:pie) for example:

```{r pie, fig.cap='A fancy pie chart.', tidy=FALSE}
par(mar = c(0, 1, 0, 1))
pie(
  c(280, 60, 20),
  c('Sky', 'Sunny side of pyramid', 'Shady side of pyramid'),
  col = c('#0292D8', '#F7EA39', '#C4B632'),
  init.angle = -50, border = NA
)
```
